### 2023-02-06 definitions.tex
Reset PN liveness undecidable confirmed, correcting some typos
up

\begin{theorem}{Adjusting theorem from ...}
The  Reset Petri Net zero reachability problem can be reduced to the liveness problem.
\end{theorem}

@@

We first modify all transitions of T_1 to include r_1 as both an input and an output.
The initial marking $\mu_2$ will include a token in $r_1$.

@@

\begin{corollary}
Reset Petri Net liveness is undecidable 
\end{corolalry}

\begin{corollary}
Reset Petri Net $t$-liveness is undecidable 
\end{corolalry}

>>>>

\begin{theorem}[Adjusting theorem from ...]
The  Reset Petri Net zero reachability problem can be reduced to the liveness problem.
\end{theorem}

@@

We first modify all transitions of $T_1$ to include $r_1$ as both an input and an output.
The initial marking $\mu_2$ will include a token in $r_1$.

@@

\begin{corollary}
Reset Petri Net liveness is undecidable 
\end{corollary}

\begin{corollary}
Reset Petri Net $t$-liveness is undecidable 
\end{corollary}
